\Title

### 2023-02-20 Grimaldi-etal-BiolCybernetics.tex
Update on Overleaf.

    	Representation of the weights for $3$ of the $32$ different learned kernels of the model as learned on natural scenes. Each pair of line correspond to the OFF and ON polarities respectively, with excitatory weights in warm colors. Delays are represented in the horizontal axis from right (zero delay) to the left (delay of $11$ steps). Because of the symmetry observed between the ON and OFF event streams, we observed that kernels are very similar for the ON polarities. These weights are associated to a specific delay on the \textit{delays} axis and to a presynaptic address defined on the two other axes. %	For the sake of clarity, the values in range $[-0.05, 0.05]$ are not shown. 

>>>>

    	Representation of the weights for $8$ directions (among the $8 \times 3$ different kernels of the model) as learned on natural scenes. Directions are shown as a red arrow on the right. The spatio-temporal kernels are represented as a sequence of images at different delays according to the horizontal axis from right (zero delay) to the left (delay of $11$ steps). Each image correspond to the weights at a given delay with excitatory and inhibitory weights in warm and cold colors, respectively. Because of the symmetry observed between the ON and OFF event streams, we observed that kernels are very similar for the ON polarities, and these are not shown here. % These weights are associated to a specific delay on the \textit{delays} axis and to a presynaptic address defined on the two other axes. %	For the sake of clarity, the values in range $[-0.05, 0.05]$ are not shown. 
